Unlocking Sensitivity for Visibility-based Estimators of the 21\,cm Reionization Power Spectrum

### 2017-10-18 Rotation paper/draft_working.tex
addressed all points and added references

Visibility-based pipelines are not fundamentally limited to using only fully redundant baselines. In fact, most sensitivity forecasts to date do include partial redundancy \citep{Pobersens, HERA, JoshAntPos}. Recently, \cite{wterm} proposed a visibility-based approach to produce power spectrum measurements using partially redundant baselines in sky-tracking measurements. Arrays capable of such tracking include MWA and LOFAR. Our work introduces a two-baseline power spectrum estimator that can be applied to both tracking-capable arrays and drift-scan telescopes such as PAPER, HERA, and potentially SKA-low.

@@

Selecting $\psi_\nu$ to be a linear function of $\nu$ allows one to cancel
%To linear order in $\nu$, $\psi_\nu$ cancels
the decoherence due to the two visibilities having different phase centers. By default the correlators of a drift-scan array phase the two visibilities both to zenith at the same time. When they are cross-multiplied with a time lag, the visibilities must be rephased before the delay transform to account for the movement of the phase center. The effect of the phase thus roughly corresponds in a shift of the delay mode measured, and we should expect $\psi_{\nu}$ to be approximately a linear function of $\nu$:
\[
\psi_{\nu}\sim 2\pi\Delta\tau\nu,
\]
where $\Delta\tau$ is a shift in delay corresponding to the phase center movement, i.e.
\[
\Delta \tau = \frac{\boldsymbol{b'}}{c}\left(\boldsymbol{\Gamma}\hat{\boldsymbol{s}}-\hat{\boldsymbol{s}}\right). 
\]

>>>>

Visibility-based pipelines are not fundamentally limited to using only fully redundant baselines. In fact, most sensitivity forecasts to date do include partial redundancy \citep{Pobersens, HERA, JoshAntPos}. \textbf{A number of methods to produce power spectrum measurements using partially redundant baselines had been studied in recent years. A power-spectrum estimator based on visibilities gridded in the $uv$-plane was introduced in \cite{Choudhury2014Estimators, Choudhury2016Taperingb, Choudhury2016Taperinga}, and compared to a simple pair-baseline estimator in \cite{Choudhury2014Estimators}. Due to considerations of computational complexity, the authors favored grid-based estimator over pair-baseline estimators despite the higher accuracy of the latter.  \cite{wterm} proposed another approach based on gridded visibilities in sky-tracking measurements. Arrays capable of tracking include MWA and LOFAR, but not drift-scan telescopes such as PAPER, HERA, and potentially SKA-low. \cite{CTrott} studied three observing strategies (tracking, zenith drift scan, and drift and shift) with a pair-visibility based approach and concluded that zenith drift scan was the preferred observing strategy. In this paper, we introduce a pair-baseline power spectrum estimator that can be applied to both tracking-capable arrays and drift scan only arrays. Our formalism also provides a way to identify the pairs to cross-correlate, overcoming the previously considered computational disadvantage as compared to grid-based estimators.
Furthermore, compared to the pair-baseline estimators studied in \cite{Choudhury2014Estimators} and \cite{CTrott}, our analysis of the sensitivities indicate the importance of the three dimensional nature of the sky, resulting in us directly addressing curved sky effects in our formalism.  }

@@

Selecting $\psi_\nu$ to be a linear function of $\nu$ allows one to cancel
%To linear order in $\nu$, $\psi_\nu$ cancels
the decoherence due to the two visibilities having different phase centers. By default the correlators of a drift-scan array phase the two visibilities both to zenith at the same time. When they are cross-multiplied with a time lag, the visibilities must be rephased before the delay transform to account for the movement of the phase center. The effect of the phase thus roughly corresponds in a shift of the delay mode measured, and we should expect $\psi_{\nu}$ to be approximately a linear function of $\nu$:
\[
\psi_{\nu}\sim 2\pi\Delta\tau\nu,
\]
where $\Delta\tau$ is a shift in delay corresponding to the phase center movement, i.e.
\[
\Delta \tau = \frac{\boldsymbol{b'}}{c}\cdot\left(\boldsymbol{\Gamma}\hat{\boldsymbol{s}}-\hat{\boldsymbol{s}}\right). 
\]
